---
title: "Case Study 01 - Beers and Breweries"
author: "Luis Garcia"
date: "2022-10-19"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

## 1. How many breweries are present in each state

```{r}

hello_breweries = read.csv("Breweries.csv")
hello_beers = read.csv("Beers.csv")

#by states
hello1=table(hello_breweries$State)
hello1
dim(hello1)
plot(hello1,main = "Breweries by state",xlab = "States", ylab = "# of Breweries",ylim=c(0,60),cex.axis = 0.5, las=2)
```

## 2. Merge beer data with the breweries data. Print the first 6 observations and the last six observations to check the merged file. (RMD only, this does not need to be included in the presentation or the deck.)
2-1.first 6 observations
```{r}
hello_merge = merge(hello_breweries,hello_beers,by.x = "Brew_ID", by.y = "Brewery_id")
head(hello_merge)
```

## 3. Address the missing values in each column.

```{r}
hello_NA = hello_merge[!complete.cases(hello_merge),]
dim(hello_NA)
head(hello_NA)
library(naniar)
gg_miss_var(hello_merge)
```

There are over 1000 missing values in IBU, almost 100 in ABV, and 5 in Style. We impute those missing values with median for our KNN prediction model.



## 4. Compute the median alcohol content and international bitterness unit for each state. Plot a bar chart to compare.

```{r, echo=FALSE, message=FALSE, results="hide"}
library(dplyr)
dplyr::summarize
hello1 <- hello_merge %>% group_by(State) %>% summarize(medianABV = median(ABV,na.rm = TRUE), count = n()) %>% arrange(medianABV)
print(hello1)
barplot(hello1$medianABV, names.arg = hello1$State, las=2 ,main = "Median ABV by state",xlab = "States", ylab = "Median ABV",cex.names = 0.5,)

hello2 <- hello_merge %>% group_by(State) %>% summarize(medianIBU = median(IBU,na.rm = TRUE), count = n()) %>% arrange(medianIBU)
print(hello2)
barplot(hello2$medianIBU, names.arg = hello2$State, las=2 ,main = "Median IBU by state",xlab = "States", ylab = "Median IBU",cex.names = 0.5)
```

## 5. Which state has the maximum alcoholic (ABV) beer? Which state has the most bitter (IBU) beer?

```{r}
hello_ABV <- hello_merge %>% group_by(State)%>%summarize(max_alc=max(ABV,na.rm=TRUE)) %>% arrange(desc(max_alc))
hello_IBU <- hello_merge %>% group_by(State)%>%summarize(max_ibu=max(IBU,na.rm=TRUE)) %>% arrange(max_ibu)
hello_ABV
hello_IBU
```

Colorado has the maximum ABV.  
Oregon has the maximum IBU.


## 6. Comment on the summary statistics and distribution of the ABV variable.

```{r}
summary(hello_merge$ABV)
hist(hello_merge$ABV,main = "Histogram of ABV",xlab = "ABV", ylab = "Count")
```

The ABV variable has a mode around .5, is right skewed, and has a range of about .11.  




## 7. Is there an apparent relationship between the bitterness of the beer and its alcoholic content? Draw a scatter plot. Make your best judgment of a relationship and EXPLAIN your answer.

```{r}
library(ggplot2)
scatter.smooth(x=hello_merge$ABV, y=hello_merge$IBU, main = "Mild positive linear relationship",xlab = "ABV", ylab = "IBU", col="blue")
```

This data shows mild positive linear relationship between bitterness and alcoholic content(3rd degree polynomial). Most of Beer bitterness comes from hops.


## 8. Budweiser KNN model ABV and IBU to predict beer style

```{r, echo=FALSE, message=FALSE, results="hide"}
library(XML) #xml_Parse
library(dplyr)
library(tidyr)
library(stringi)
library(rvest) #html_table, html_node
library(ggplot2)
library(RCurl) #getURL
library(class)
library(caret)
library(e1071)
#install.packages("Hmisc")
library(Hmisc)
#install.packages("stringr")     # Install & load stringr package
library("stringr")
library(naniar)

#classfy IPAs or not, using IBU and ABV values.
#make new column as IPAs and the values will be 1 or 0. When the Style has "IPA", the value will be 1. nor 0.
#hello_IPA <- 1*str_detect(hello_merge$Style, "IPA")
hello_IPAs = ifelse(str_detect(hello_merge$Style,"IPA")==TRUE,"IPA",ifelse(str_detect(hello_merge$Style,"Ale")==TRUE,"ALE","Other"))
hello_merge$Beer_type <- hello_IPAs
head(hello_merge)


hello_merge %>% ggplot(aes(x = ABV, y = IBU, color=Beer_type)) + 
geom_point() +
stat_ellipse()

#median IPA
hello_filter1=filter(hello_merge, Beer_type == "IPA")
median(hello_filter1$ABV[which(!is.na(hello_filter1$ABV))])
median(hello_filter1$IBU[which(!is.na(hello_filter1$IBU))])

#median Ale
hello_filter2=filter(hello_merge, Beer_type == "ALE")
median(hello_filter2$ABV[which(!is.na(hello_filter2$ABV))])
median(hello_filter2$IBU[which(!is.na(hello_filter2$IBU))])

#median no IPA
hello_filter3=filter(hello_merge, Beer_type == "Other")
median(hello_filter3$ABV[which(!is.na(hello_filter3$ABV))])
median(hello_filter3$IBU[which(!is.na(hello_filter3$IBU))])


#impute missing values with median
hello_impute <- hello_merge
hello_impute$IBU <- impute(hello_impute$IBU, median)
hello_impute$ABV <- impute(hello_impute$ABV, median)
hello_impute = hello_impute[complete.cases(hello_impute),]
gg_miss_var(hello_impute)

#scaling
hello_scale = hello_impute
hello_scale$IBU = scale(hello_impute$IBU)
hello_scale$ABV = scale(hello_impute$ABV)
hello_scale %>% ggplot(aes(x = ABV, y = IBU, color=Beer_type)) + 
geom_point() +
stat_ellipse()
```

```{r}
#70/30 training/
# Loop for many k and the average of many training / test partition

set.seed(100)
iterations = 10
numks = 20
splitPerc = .70

masterAcc = matrix(nrow = iterations, ncol = numks)


for(j in 1:iterations)
{
  trainIndices = sample(1:dim(hello_scale)[1],round(splitPerc * dim(hello_scale)[1]))
  train = hello_scale[trainIndices,]
  test = hello_scale[-trainIndices,]
  for(i in 1:numks)
  {
    classifications = knn(train[,c(7,8)],test[,c(7,8)],train$Beer_type, prob = TRUE, k = i)
    table(classifications,test$Beer_type)
    CM = confusionMatrix(table(classifications,test$Beer_type))
    masterAcc[j,i] = CM$overall[1]
  }
  
}

MeanAcc = colMeans(masterAcc)

plot(seq(1,numks,1),MeanAcc, type = "l")

which.max(MeanAcc)
max(MeanAcc)
```

```{r}
## Accuracy was used to select the optimal model using the largest value.
## The final value used for the model was k = 20.
classifications = knn(train[,c(7,8)],test[,c(7,8)],train$Beer_type, prob = TRUE, k = 5)
table(classifications,test$Beer_type)
CM = confusionMatrix(table(classifications,test$Beer_type))
CM
```

```{r}
#decision boundary
prob1 <- attr(classifications, "prob")
px1 <- test$ABV
px2 <- test$IBU


mat = matrix(, nrow = 723, ncol = 3)
mat[,1] <- px1
mat[,2] <- px2
mat[,3] <- classifications

dff <- data.frame(mat)
colnames(dff) <- c('var1', 'var2', 'var3')

ggplot(dff)+geom_point(aes(x = var1, y = var2, col=var3))+
geom_contour(aes(x = var1, y = var2, z = var3))
```

```{r}
#input
biterness = 100
alchol = 0.089

#scale
scaled_center_biterness = 39.49668
scaled_scale_biterness = 20.17576
scaled_center_alc = 0.05967635
scaled_scale_alc = 0.01337969

y=(biterness-scaled_center_biterness)/scaled_scale_biterness
x=(alchol-scaled_center_alc)/scaled_scale_alc
test1= c(x,y)
knn(train[,c(7,8)],test1,train$Beer_type, prob = TRUE, k = 5)

```


## 9. Knock their socks off! Find one other useful inference from the

data that you feel Budweiser may be able to find value in. You must
convince them why it is important and back up your conviction with
appropriate statistical evidence.

```{r}
##market share, beers by breweries
freq_table=table(hello_merge$Brew_ID)
hello_market <- hello_merge %>% group_by(Brew_ID)%>%tally(sort = TRUE)
#add state on column
hello_market <- as.data.frame(hello_market)
df2 = merge(hello_market,hello_breweries,by.x = "Brew_ID")%>% arrange(desc(n))
head(df2)
#add median 
means3abv= hello_merge %>% filter(Brew_ID == 11 | Brew_ID == 26 | Brew_ID == 167) %>% group_by(Brew_ID) %>% summarise(meanABV = mean(ABV,na.rm = TRUE), count = n())

means3ibu=hello_merge %>% filter(Brew_ID == 11 | Brew_ID == 26 | Brew_ID == 167) %>% group_by(Brew_ID) %>% summarise(meanIBU = mean(IBU,na.rm = TRUE), count = n())

bestmeanibu = mean(c(42.90625,66.40000))

bestmeanabv = mean(c(0.06998333,0.06933333,0.07389655))
```

The breweries who has most beers is Brewery Vivant in MI. The Sun King Brewing Company in IN and Oskar Blues Brewery in CO is 2nd and 3rd.

what is the best, optimized ABV and IBU in Texas market compared to the best three markets?
From our analysis of the mean of the three top breweries, we see that the best mean ABV and IBU value are .07107 and 54.65313.
